---
title: "Influence of Time Since HIV Diagnosis on Seeking Health Information Online"
author: "Adam Northrup"
date: "March 19, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.align = "center",
                      echo = FALSE, include = FALSE, 
                      warning = FALSE, message = FALSE)
# install and load required packages
if (!require("pacman")) 
  install.packages("pacman", repos='http://cran.us.r-project.org')
p_load("tidyverse", "R2jags", "knitr", "kableExtra", "lattice", "gridExtra")
setwd("C:/Users/anthe/Google Drive/MS Biostats/Courses/06 2019 Winter/BS 234/Bayes_FinalDAP")
theme_set(theme_bw())

load("C:/Users/anthe/Google Drive/MS Biostats/Courses/06 2019 Winter/BS 234/Labs/AddBurnin.RData")
load("model_all.RData")
```
<div style="line-height: 2em;">
## Abstract  
This analysis will determine whether time since HIV diagnosis plays a role in whether an HIV-positive youth seeks health information online. Data constitutes responses from surveys administered to patients at 10 clinical sites across the country. The effect of time since diagnosis will be evaluated when controlling for as age, race, gender, sexual orientation, education, and employment status. The event of interest, y, is a binary event, and can be characterized by the probability of the event ($\pi$). The effect of time will be measured using logistic regression, and will take the form of an odds ratio, $e^{\alpha}$. $\alpha$ is a vector of regression coefficients. Regression coefficients are expected to follow different normal distributions, with expectations taken from prior research. Survey results from each each site may be correlated, and so a site-specific effect will be considered.  

## Introduction  
Investigators are interested in health-information seeking behavior in order to better adapt interventions geared toward HIV positive youth. The purpose of the survey is ultimately to determine factors that encourage participants to take an active role in their health care. This analysis will determine if one such factor, time since HIV diagnosis, has an effect on health-seeking behavior.  

## Methods  
### Data  
Data comes from the Health Resources and Services Administration's Special Projects of National Significance Initiative, Use of Social Media to Improve Engagement, Retention, and Health Outcomes along the HIV Care Continuum. Participant and site identifying information have been removed. Participants were HIV positive youth and young adults (ages 16-34), and data were self-reported by participants between 2016 and 2018. Sites are located in major cities, distributed across the United States. Participants at sites have different demographic makeup, and while these demographics will be controlled for, it is thought that there may be correlation among participants within site. Data consists of a baseline survey taken upon entrance into the study, and a 6-month follow-up.  

The outcome, `HealthInfo` is a binary variable, indicating whether a participant has reported looking for health-related information online. There are multiple types of health information that participants may report searching for, including cold/flu symptoms, transgender therapies, and STD information. If participants responded affirmatively to any of these, `HealthInfo` is recorded as a 1, otherwise a 0. Since these questions are asked in the 6-month follow-up, participants that were lost to follow-up are not included in this analysis. Ideally, $\chi^2$ testing would be performed between those participants included and those lost to follow-up, but those lost to follow-up were not included in the data set.  

Demographic information was taken from the baseline survey. Some participants were given only a 6-month survey and no baseline survey, thus they were not included in the data set.  

Of the available covariates, only `SINCEHIV` (time since HIV diagnosis), and `Age` are continuous. Figure 1 shows the distribution for `Age` broken down by whether participants sought health information. Figure 2 shows the distribution for `SINCEHIV` and the log of `SINCEHIV`.  

Variables for gender, sexual orientation, ethnicity, race, and education are coded as binary variables with numerous options that were pared down for the purposes of this analysis. Employment status was not already coded as binary, and so had to be treated differently, as detailed below. Demographic covariates were collapsed to reflect categories for which prior information was available. 

Gender was reduced to male, female, and 'other' categories. Cis and trans men were collapsed together, and the same for women. A new variable, `LGBTQ` was created from gender and sexual orientation, indicating whether participant is LGBGTQ or non-LGBTQ. 

Participants who indicated latino were marked as latino, and the rest were broken into different race categories. Categories were created for black non-latinos, white non-latinos, and others.  

Education was reduced to high school or high school equivalent or less, and more than a high school education.  

The employment status question of the survey allowed participants to check all that apply, including: student, full-time or part-time employed, on disability, unemployed and looking for work, or unemployed and not looking. In order to code employment in dummy variables, these were collapsed into fewer categories and the different combinations were evaluated, with the most infrequent collapsed into an other category. The remaining categories include student, employed, disabled, and unemployed. Student includes employed and unemployed students. Other combinations were rare.  

Demographic information of participants is summarized in Table 1. There are 686 participants included in the analysis, of which 627 are LGBTQ, 498 are men, 167 women, 197 are Latino, 329 are black (not Latino), and 116 are white (not Latino). Approximately half had more than high school educations, 294 are employed, and 254 are unemployed. Number of each who sought out health information online is also documented in Table 1. 

```{r data, eval = FALSE}
acasi3 <- acasi2 %>%
  filter(!is.na(SCREEN1)) %>%
  filter(BORNHIV == 0) %>%
  arrange(SITE1) %>%
  mutate(Site = as.numeric(as.factor(SITE1)),
         ID = 1:n(),
         HealthInfo = if_else(S56_24XL + S56_24XM + S56_24XN + S56_24XO > 0 &
                                S56_24XL + S56_24XM + S56_24XN + S56_24XO < 8,
                              1, 0)) %>%
  select(Site, ID, BORNHIV, DIAGHIV, SCREEN1, ORIENT, GENDER, GRADE, 
         LATINO, starts_with("RACE"), -RACE, -RACEFS,
         contains("EMPLOY"), -EMPLOY, -EMPLOYE, -EMPLOYF, HealthInfo) %>%
  mutate_at(vars(RACE_RC, ORIENT, GENDER, GRADE, starts_with("EMPLOY")),
            funs(as.factor)) %>%
  mutate(SINCEHIV = 2019 - DIAGHIV,
         LGBTQ = if_else(ORIENT == 1 & GENDER %in% c(1, 2), 0, 1),
         GENDER_RC = fct_recode(GENDER,
                                 "Man"              = "1", 
                                 "Woman"            = "2",
                                 "Man"              = "3", 
                                 "Woman"            = "4",
                                 "Other gender"     = "5", 
                                 "Other gender"     = "6",
                                 "Refuse to answer" = "8"),
         GRADE_RC = fct_recode(as.factor(GRADE),
                               "High school, equivalent or less"  = "1", 
                               "High school, equivalent or less"  = "2", 
                               "High school, equivalent or less"  = "3", 
                               "More than high school"            = "4", 
                               "More than high school"            = "5", 
                               "More than high school"            = "6",
                               "More than high school"            = "7", 
                               "Refuse to answer"                 = "8"),
         RACE_RC = case_when(LATINO == 1 ~ "Latino",
                             RACEC == 1 ~ "Black, Not Latino",
                             RACEE == 1 ~ "White, Not Latino",
                             TRUE ~ "Other race"),
         EMPLOYB_RC = if_else(EMPLOYB == 1 | EMPLOYC == 1, 1, 0),
         EMPLOYA = fct_recode(EMPLOYA, "A" = "1"),
         EMPLOYB_RC = fct_recode(as.factor(EMPLOYB_RC), "B" = "1"),
         EMPLOYD = fct_recode(EMPLOYD, "D" = "1"),
         EMPLOYE_RC = fct_recode(EMPLOYE_RC, "E" = "1"),
         EMPLOY = str_replace_all(
           paste0(EMPLOYA, EMPLOYB_RC, EMPLOYD, EMPLOYE_RC),
           "0", ""
         ),
         EMPLOY = fct_lump(as.factor(EMPLOY), n = 5),
         EMPLOY = fct_recode(EMPLOY,
                             "Student" = "A",
                             "Student" = "AB",
                             "Employed" = "B",
                             "Disabled" = "D",
                             "Unemployed" = "E")) %>%
  select(Site, ID, HealthInfo, SINCEHIV, SCREEN1, LGBTQ, GENDER_RC, 
         GRADE_RC, RACE_RC, EMPLOY) %>%
  rename(Age = SCREEN1)

y <- acasi3$HealthInfo
x <- acasi3 %>%
  mutate(Intercept = 1,
         Gender_Woman = if_else(GENDER_RC == "Woman", 1, 0),
         Gender_Other = if_else(GENDER_RC == "Other gender", 1, 0),
         Ed_Higher = if_else(GRADE_RC == "More than high school", 1, 0),
         Race_Black = if_else(RACE_RC == "Black, Not Latino", 1, 0),
         Race_White = if_else(RACE_RC == "White, Not Latino", 1, 0),
         Race_Other = if_else(RACE_RC == "Other race", 1, 0),
         Employ_Student = if_else(EMPLOY == "Student", 1, 0),
         Employ_Employed = if_else(EMPLOY == "Employed", 1, 0),
         Employ_Disabled = if_else(EMPLOY == "Disabled", 1, 0),
         Employ_Other = if_else(EMPLOY == "Other", 1, 0)) %>%
  select(Intercept, SINCEHIV, Age, starts_with("Gender_"), Ed_Higher, 
         starts_with("Race_"), starts_with("Employ_"),
         -GENDER_RC, -RACE_RC) %>%
  as.matrix()
```

```{r summary}
#####Create summary tables
#Functions
tab1_OneFactor <- function (x, varString, varRelevel = NULL) {
  varQuo <- enquo(varString)
  x %>%
    select(HealthInfo, !!varQuo) %>%
    group_by(!!varQuo) %>%
    summarize(N = n(),
              P = n() / nrow(.),
              N.y = sum(HealthInfo),
              P.y = sum(HealthInfo) / length(HealthInfo)) %>%
    arrange(desc(N)) %>%
    mutate(`Sample Frequency` = paste0(N, 
                                       " (", 
                                       scales::percent(P, accuracy = 0.1),
                                       ")"),
           `Seeking Health Info` = paste0(N.y, 
                                       " (", 
                                       scales::percent(P.y, accuracy = 0.1),
                                       ")")) %>%
    rename(Variable = !!varQuo) %>%
    select(-N, - P, -N.y, -P.y) %>%
    mutate(Variable = fct_relevel(factor(Variable, levels = unique(Variable)), 
                                  varRelevel)) %>%
    arrange(Variable) %>%
    mutate(Variable = as.character(Variable))
}

tab1_ManyBinary <- function (x, ..., response = 1) {
  selectVars <- quos(...)
  x %>%
    select(HealthInfo, !!!selectVars) %>%
    gather("Variable", "Value", -HealthInfo) %>%
    group_by(Variable) %>%
    summarize(N = sum(Value),
              P = sum(Value) / n(),
              N.y = sum(HealthInfo[which(Value == 1)]),
              P.y = sum(HealthInfo[which(Value == 1)]) / 
                length(HealthInfo[which(Value == 1)])) %>%
    arrange(desc(N)) %>%
    mutate(`Sample Frequency` = paste0(N, 
                                       " (", 
                                       scales::percent(P, accuracy = 0.1),
                                       ")"),
           `Seeking Health Info` = paste0(N.y, 
                                       " (", 
                                       scales::percent(P.y, accuracy = 0.1),
                                       ")")) %>%
    select(-N, - P, -N.y, -P.y)
}

#Create summary table
demo <- acasi3 %>%
  mutate(LGBTQ = fct_recode(as.factor(LGBTQ),
                            "Non-LGBTQ" = "0", 
                            "LGBTQ" = "1"))

table1 <- bind_rows(
  demo %>%
      summarize(Variable = "Number of participants",
                `Sample Frequency` = as.character(n())),
  bind_rows(
    demo %>%
      summarize(Variable = "Age",
                Mean = mean(Age),
                SD = sd(Age)),
    demo %>%
      summarize(Variable = "Time since HIV diagnosis",
                Mean = mean(SINCEHIV),
                SD = sd(SINCEHIV))
  ) %>%
    mutate_if(is.numeric, funs(round), 1) %>%
    unite("Sample Frequency", Mean, SD, sep = " (") %>%
    mutate(`Sample Frequency` = paste0(`Sample Frequency`, ")")),
  tab1_OneFactor(demo, varString = LGBTQ),
  tab1_OneFactor(demo, varString = GENDER_RC),
  tab1_OneFactor(demo, varString = RACE_RC) %>%
    mutate(Variable = fct_relevel(factor(Variable, levels = unique(Variable)),
                                  "Latino")) %>%
    arrange(Variable) %>%
    mutate(Variable = as.character(Variable)),
  tab1_OneFactor(demo, varString = GRADE_RC),
  tab1_OneFactor(demo, varString = EMPLOY)
)

demoPlots <- demo %>%
  mutate(HealthInfo = fct_recode(as.factor(HealthInfo),
                                 "Seeks Info" = "1",
                                 "Does Not Seek Info" = "0"))
plotAge <- ggplot(demoPlots, aes(x = Age, fill = factor(HealthInfo))) +
  geom_histogram(binwidth = 1, show.legend = FALSE) +
  facet_grid(~HealthInfo) +
  labs(y = "Count", title = "Distribution of Age Stratified by Health Information Seeking")
plotSINCEHIV <- ggplot(demoPlots, aes(x = SINCEHIV, fill = factor(HealthInfo))) +
  geom_histogram(binwidth = 1, show.legend = FALSE) +
  facet_grid(~HealthInfo) +
  labs(y = "Count", title = "Distribution of Time Since HIV Diagnosis Stratified by Outcome")
plotSINCEHIVlog <- ggplot(demoPlots, aes(x = log(SINCEHIV), fill = factor(HealthInfo))) +
  geom_histogram(binwidth = .33, show.legend = FALSE) +
  facet_grid(~HealthInfo) +
  labs(y = "Count", title = "Distribution of log of Time Since HIV Diagnosis Stratified by Outcome")

plotCorr <- ggplot(demoPlots, aes(x = Age, y = SINCEHIV, color = HealthInfo)) +
  geom_point(position = position_jitter(), show.legend = FALSE) +
  facet_grid(~HealthInfo) +
  labs(y = "Time Since HIV Diagnosis (yr)", x = "Age (yr)",
       title = "Age Against Time Since Diagnosis, Separated by Outcome")

corAgeSinceHIV <- cor(x[, 2:3])[1, 2]
table2 <- tibble(Parameter = colnames(x), 
                 alpha = paste0("alpha[", 1:13, "]"),
                 Mean = c("0", "-1", "1", "1", "1", "1", 
                          "0", "0", "0", "1", "1", "1", "0"),
                 SD = rep(1, 13))

```

### Models
Four models were evaluated and compared to determine the effect of `SINCEHIV`. The first model included `Age`, but since `Age` was found to be correlated with `SINCEHIV`, ($\rho$ = `r round(corAgeSinceHIV, 2)`, Figure 1), a second model without `Age` was considered. Both of these models included `Site` as a random effect, as participant outcomes were anticipated to be correlated within site. The third model did not include `Age` or random effects. The third model would include `Age` if the first model is shown to outperform the second model without `Age`. The fourth model was similar to the second, except used the log of `SINCEHIV`. Models followed the general form:  
$$
Y_i \sim Bernoulli(\pi_i) \\
log \frac{\pi_i}{1 - \pi_i} = x_i^T\alpha + \beta_{j} 
$$
with the following distributions:  
$$
\beta_j ~ Norm_o(0, \tau_b) \\
\tau_b ~ Gamma(0.25, 0.25) \\
\alpha_k ~ Norm(\mu_k, 1)
$$

Regression coefficients were expected to follow normal distributions, though these distributions are unknown. They were generally estimated to be likely negative, zero, or positive, with means of -1, 0, or 1 and standard deviation of 1. This allows each distribution to include zero. Prior information was taken from Rideout and Fox, 2018, which assessed the effects of age, gender, LGBTQ status, and race. Effects of education and employment status were not detailed. See Table 2 for prior normal distribution parameters. `SINCEHIV` was expected to have a negative effect, given newly diagnosed participants were thought likely to attempt to learn about their diagnosis. Rideout and Fox reported higher likelihood of seeking health information with increased age, for women and LGBTQ over men and non-LGBTQ. Race was reported as having no effect. It was estimated that participants with higher education and employment would have increased likelihood of seeking health information.  

The model that best converged and had the lowest DIC was selected. Initial iterations were set to 1100 with 100 burnin and thinning of 1. Convergence was assessed and sensitivity analysis performed for Models 1 and 2 prior to initiating model 3. Sensitivity analysis included increasing iterations and thinning. Poor convergence may also necessitate changing precision levels for random effects. Once a model is selected, linearity will be assessed and any necessary transformations will be made. The effects of `SINCEHIV` will then be determined.  

## Results  
Models 1 and 2 had high autocorrelation and high spikes in time series plots. Iterations were increased to 5100 with thinning of 5, and then again to 8100 with thinning of 8. Burnin was never increased because models appeared to converge quickly. The models with 8100 iterations were not noticeably different from those with 5100, and so the models with 5100 were compared. Figure 3 shows autocorrelation and convergence of random effects $\sigma_b$ for all four models. Autocorrelation and convergence for $\alpha$ coefficients were also compared, but only those for Model 4 are shown (Figures 4 and 5). Autocorrelation is lower for Model 3, though convergence is poor, by orders of magnitude. Autocorrelation is similar and slightly higher for Models 1, 2, and 3, but convergence is good. Models 1, 2, and 3 are indistinguishable graphically, but model 4 has the lowest DIC (Table 3), so Model 4 appears to be the best-performing. Convergence for $\alpha$ in Figure 5 is good for all covariates.  

Model 2 and model 4 were assessed for linearity in the continuous variable, `SINCEHIV`. Figure 6 shows Model 2 (top) and Model 4 (bottom) `SINCEHIV` plotted against $\pi_i$ and $y_i$ with LOESS smoothers for each. The curves are similar, though they differ at specific values of `SINCEHIV`. For Model 2, it is possible that due to the low number of observations at the high end of the curve, the differences are due to noise. The differences in the middle (near 11 years) may also be due to the upward tail of the LOESS curve on `HealthInfo` at high values. The differences in the two curves at values of `SINCEHIV` under 5 years lend possible evidence against the fit of the model. Generally the probability of seeking health information, $\pi$, is high for lower times since HIV diagnosis, and the same is true for number of participants seeking health information, y. However, $\pi$ is higher than y at 1 year according to the LOESS curve. The slight dip in both curves at 4 years also takes away from the linearity of the model for this covariate. Model 4 was created in order to account for these differences in LOESS curves. Model 4 has similar curves, but with slightly closer tails on the low end of `SINCEHIV`. These differences should still be noted as a potential limitation of the model.  

The $\alpha$ coefficient for time since diagnosis (`SINCEHIV`) on whether a participant sought health information online is seen in Table 4 as -0.40. Table 4 also includes the coefficients for other covariates, but the effects of these covariates were not of interest in the research question. The estimate for the SD for the random effect distribution is also listed.  

## Conclusions  


## Appendix
### Model 1  
This model includes 13 covariates including `Age`, with regression coefficients (alpha), and random effects (beta).  
```{r model1, echo = TRUE, include = TRUE}
cat(
"model{
  for (i in 1:N.obs) {
		y[i] ~ dbern(pie[i])
    logit(pie[i]) <- inprod(x[i, ], alpha[]) + beta[site[i]]
  }
  for (j in 1:N.sites) {
    beta[j] ~ dnorm(0, tau)
  }
  alpha[1] ~ dnorm(mu[1], tau.a)
  alpha[2] ~ dnorm(mu[2], tau.a)
  alpha[3] ~ dnorm(mu[3], tau.a)
  alpha[4] ~ dnorm(mu[4], tau.a)
  alpha[5] ~ dnorm(mu[5], tau.a)
  alpha[6] ~ dnorm(mu[6], tau.a)
  alpha[7] ~ dnorm(mu[7], tau.a)
  alpha[8] ~ dnorm(mu[8], tau.a)
  alpha[9] ~ dnorm(mu[9], tau.a)
  alpha[10] ~ dnorm(mu[10], tau.a)
  alpha[11] ~ dnorm(mu[11], tau.a)
  alpha[12] ~ dnorm(mu[12], tau.a)
  alpha[13] ~ dnorm(mu[13], tau.a)
  tau ~ dgamma(b1, b2)
  sigma <- 1/ tau
}",
  fill = TRUE,
	file = "model1_logit_mixed.txt")
```

### Model 2  
This model does not include `Age`, indicated by 12 regression coefficients (alpha). This model includes random effects for `Site` (beta).  
```{r model2, echo = TRUE, include = TRUE}
cat(
"model{
  for (i in 1:N.obs) {
		y[i] ~ dbern(pie[i])
    logit(pie[i]) <- inprod(x[i, ], alpha[]) + beta[site[i]]
  }
  for (j in 1:N.sites) {
    beta[j] ~ dnorm(0, tau)
  }
  alpha[1] ~ dnorm(mu[1], tau.a)
  alpha[2] ~ dnorm(mu[2], tau.a)
  alpha[3] ~ dnorm(mu[3], tau.a)
  alpha[4] ~ dnorm(mu[4], tau.a)
  alpha[5] ~ dnorm(mu[5], tau.a)
  alpha[6] ~ dnorm(mu[6], tau.a)
  alpha[7] ~ dnorm(mu[7], tau.a)
  alpha[8] ~ dnorm(mu[8], tau.a)
  alpha[9] ~ dnorm(mu[9], tau.a)
  alpha[10] ~ dnorm(mu[10], tau.a)
  alpha[11] ~ dnorm(mu[11], tau.a)
  alpha[12] ~ dnorm(mu[12], tau.a)
  tau ~ dgamma(b1, b2)
  sigma <- 1/ tau
}",
  fill = TRUE,
	file = "model2_logit_mixed.txt")
```

### Model 3  
This model does not include `Age` (see only 12 alphas) or random effects.  
```{r model3, echo = TRUE, include = TRUE}
cat(
"model{
  for (i in 1:N.obs) {
		y[i] ~ dbern(pie[i])
    logit(pie[i]) <- inprod(x[i, ], alpha[])
  }
  alpha[1] ~ dnorm(mu[1], tau.a)
  alpha[2] ~ dnorm(mu[2], tau.a)
  alpha[3] ~ dnorm(mu[3], tau.a)
  alpha[4] ~ dnorm(mu[4], tau.a)
  alpha[5] ~ dnorm(mu[5], tau.a)
  alpha[6] ~ dnorm(mu[6], tau.a)
  alpha[7] ~ dnorm(mu[7], tau.a)
  alpha[8] ~ dnorm(mu[8], tau.a)
  alpha[9] ~ dnorm(mu[9], tau.a)
  alpha[10] ~ dnorm(mu[10], tau.a)
  alpha[11] ~ dnorm(mu[11], tau.a)
  alpha[12] ~ dnorm(mu[12], tau.a)
  tau ~ dgamma(b1, b2)
  sigma <- 1/ tau
}",
  fill = TRUE,
	file = "model3_logit_fixed.txt")
```

```{r runMod1, eval = FALSE}
parameters <- c("pie", "alpha", "beta", "sigma")

initsMod1 <- rep(
  list(
    list(
      alpha = rep(0, 13),  
      beta  = rep(0, length(unique(acasi3$Site))),  
      tau   = 1)
  ),
  5
)

priorDataMod1 = list(N.obs = nrow(acasi3), 
                     N.sites = length(unique(acasi3$Site)),
                     site = acasi3$Site,
                     b1 = 0.25, 
                     b2 = 0.25,
                     mu = table2$Mean,
                     tau.a = 1,
                     y = y, 
                     x = x)
proc.time()
runMod1 = jags(priorDataMod1, initsMod1, parameters, 
               "model1_logit_mixed.txt", 
               n.chains = 5, n.iter = 5100, n.burnin = 0, n.thin = 1)
proc.time()
burnMod1 <- AddBurnin(runMod1$BUGSoutput$sims.array, 
                      burnin = 100, n.thin = 5)
dicMod1 <- runMod1$BUGSoutput$DIC
```

```{r runMod2, eval = FALSE}
initsMod2 <- rep(
  list(
    list(
      alpha = rep(0, 12),  
      beta  = rep(0, length(unique(acasi3$Site))),  
      tau   = 1)
  ),
  5
)

priorDataMod2 = list(N.obs = nrow(acasi3), 
                     N.sites = length(unique(acasi3$Site)),
                     site = acasi3$Site,
                     b1 = 0.25, 
                     b2 = 0.25,
                     mu = table2$Mean[-3],
                     tau.a = 1,
                     y = y, 
                     x = x[, -3])
proc.time()
runMod2 = jags(priorDataMod2, initsMod2, parameters, 
               "model2_logit_mixed.txt", 
               n.chains = 5, n.iter = 5100, n.burnin = 0, n.thin = 1)
proc.time()
burnMod2 <- AddBurnin(runMod2$BUGSoutput$sims.array, 
                      burnin = 100, n.thin = 5)
dicMod2 <- runMod2$BUGSoutput$DIC
```

```{r runMod3, eval = FALSE}
initsMod3 <- rep(
  list(
    list(
      alpha = rep(0, 12),  
      tau   = 1)
  ),
  5
)

priorDataMod3 = list(N.obs = nrow(acasi3), 
                     b1 = 0.25, 
                     b2 = 0.25,
                     mu = table2$Mean[-3],
                     tau.a = 1,
                     y = y, 
                     x = x[, -3])
proc.time()
runMod3 = jags(priorDataMod3, initsMod3, parameters, 
               "model3_logit_fixed.txt", 
               n.chains = 5, n.iter = 5100, n.burnin = 0, n.thin = 1)
proc.time()
burnMod3 <- AddBurnin(runMod3$BUGSoutput$sims.array, 
                      burnin = 100, n.thin = 5)
dicMod3 <- runMod3$BUGSoutput$DIC
```

```{r runMod4, eval = FALSE}
x4 <- x[ , -3]
x4[, 2] <- log(x4[, 2])
priorDataMod4 = list(N.obs = nrow(acasi3), 
                     N.sites = length(unique(acasi3$Site)),
                     site = acasi3$Site,
                     b1 = 0.25, 
                     b2 = 0.25,
                     mu = table2$Mean[-3],
                     tau.a = 1,
                     y = y, 
                     x = x4)
proc.time()
runMod4 = jags(priorDataMod4, initsMod2, parameters, 
               "model2_logit_mixed.txt", 
               n.chains = 5, n.iter = 5100, n.burnin = 0, n.thin = 1)
proc.time()
burnMod4 <- AddBurnin(runMod4$BUGSoutput$sims.array, 
                      burnin = 100, n.thin = 5)
dicMod4 <- runMod4.1$BUGSoutput$DIC

```

</div>
```{r summaryTable, include = TRUE}
kable(table1, caption = "Table 1. Participant Characteristics") %>%
  kable_styling(bootstrap_options = c("striped", "condensed"),
                full_width = FALSE) %>%
  group_rows("Continuous Variables, Mean (SD)", 2, 3) %>%
  group_rows("LGBTQ Status, Number (%) of Participants", 4, 5) %>%
  group_rows("Gender, Number (%) of Participants", 6, 8) %>%
  group_rows("Ethnicity and Race, Number (%) of Participants", 9, 12) %>%
  group_rows("Education, Number (%) of Participants", 13, 14) %>%
  group_rows("Employment Status, Number (%) of Participants", 15, 19)

kable(table2, caption = "Table 2. Prior Normal Parameters") %>%
  kable_styling(bootstrap_options = c("striped", "condensed"),
                full_width = FALSE)
```

```{r plotAge, include = TRUE, fig.cap = "Figure 1. Distribution of Participant Age, Age against SINCEHIV"}
grid.arrange(plotAge, plotCorr)
```

```{r plotSINCEHIV, include = TRUE, fig.cap = "Figure 2. Distribution of SINCEHIV and log(SINCEHIV)"}
grid.arrange(plotSINCEHIV, plotSINCEHIVlog)
```

```{r jagsPlotsSigma, include = TRUE, fig.cap = "Figure 3. Autocorrelation and Convergence of Sigmas"}
plotACF <- function (burn, n, parameter, name = parameter, 
                     model = NULL, lag.max = NULL) {
  for(i in 1:length(parameter)) {
    acf(burn$Burnin.sims.matrix[1:n, parameter[1]], lag.max = lag.max, 
        main = paste(model, name[i]))
  }
}
plotTime <- function (burn, n, parameter, name = parameter, model = NULL, ylim = NULL) {
  for(i in 1:length(parameter)) {
    plot(1:n, burn$Burnin.sims.matrix[1:n, parameter[1]], type = "l", 
         main = paste(model, name[i]), ylab = parameter[i], xlab = "Iteration",
         ylim = ylim)
  }
}
par(mfrow = c(2, 4))
plotACF(burnMod1, n = 1000, parameter = "sigma", model = "Model 1")
plotACF(burnMod2, n = 1000, parameter = "sigma", model = "Model 2")
plotACF(burnMod3, n = 1000, parameter = "sigma", model = "Model 3")
plotACF(burnMod4, n = 1000, parameter = "sigma", model = "Model 4")
plotTime(burnMod1, n = 1000, parameter = "sigma", model = "Model 1", ylim = c(0, 3))
plotTime(burnMod2, n = 1000, parameter = "sigma", model = "Model 2", ylim = c(0, 3))
plotTime(burnMod3, n = 1000, parameter = "sigma", model = "Model 3", ylim = c(0, 3))
plotTime(burnMod4, n = 1000, parameter = "sigma", model = "Model 4", ylim = c(0, 3))
```

```{r dicTable, include = TRUE}
kable(tibble(Model = c("Model 1", "Model 2", "Model 3", "Model 4"),
             DIC = c(dicMod1, dicMod2, dicMod3, dicMod4)), 
      digits = 1,
      caption = "Table 3. Model DIC") %>%
  kable_styling(bootstrap_options = c("striped", "condensed"),
                full_width = FALSE)

```

```{r jagsPlotsAlpha1, include = TRUE, fig.cap = "Figure 4. Autocorrelation and Convergence of Model 2 Alphas 1-6"}
par(mfrow = c(2, 3))
plotACF(burnMod2, n = 1000, paste0("alpha[", 1:6, "]"), 
        table2$Parameter[c(1, 2, 4:7)], "Model 2")
plotACF(burnMod2, n = 1000, paste0("alpha[", 7:12, "]"), 
        table2$Parameter[8:13], "Model 2")
```

```{r jagsPlotsAlpha2, include = TRUE, fig.cap = "Figure 5. Autocorrelation and Convergence of Model 2 Alphas 7-12"}
par(mfrow = c(3, 2))
plotTime(burnMod2, n = 1000, paste0("alpha[", 1:6, "]"), 
         table2$Parameter[c(1, 2, 4:7)], "Model 2")
plotTime(burnMod2, n = 1000, paste0("alpha[", 7:12, "]"), 
         table2$Parameter[8:13], "Model 2")
```

```{r diagnosticsMod2, include = TRUE, fig.cap = "Figure 6. Model Diagnostics"}
sumMod2 <- burnMod2$Burnin.sims.matrix %>%
  as.data.frame() %>%
  gather("Parameter", "Value") %>%
  group_by(Parameter) %>%
  summarize(Mean = mean(Value),
            SD = sd(Value),
            `2.5%` = quantile(Value, 0.025),
            `97.5%` = quantile(Value, 0.975),
            `P>0` = length(which(Value > 0)) / length(Value),
            `P<0` = length(which(Value < 0)) / length(Value)) %>%
  mutate(Name = str_replace(Parameter, "(.*)(\\[.*)", "\\1"),
         Number = as.numeric(str_replace(Parameter, 
                                         "(.*\\[)(\\d+)(\\])", "\\2"))) %>%
  arrange(Name, Number) %>%
  select(-Name, -Number)
alphaMod2 <- sumMod2$Mean[str_detect(sumMod2$Parameter, "alpha")]
betaMod2 <- sumMod2$Mean[str_detect(sumMod2$Parameter, "beta")]
piMod2 <- sumMod2$Mean[str_detect(sumMod2$Parameter, "pie")]
diagMod2 <- tibble(y = y,
                   pi = piMod2, 
                   logitPi = log(pi / (1 - pi)),
                   SINCEHIV = x[, 2],
                   a2 = alphaMod2[2],
                   color = "1") %>%
  mutate(xa = SINCEHIV * a2)

sumMod4 <- burnMod4$Burnin.sims.matrix %>%
  as.data.frame() %>%
  gather("Parameter", "Value") %>%
  group_by(Parameter) %>%
  summarize(Mean = mean(Value),
            SD = sd(Value),
            `2.5%` = quantile(Value, 0.025),
            `97.5%` = quantile(Value, 0.975),
            `P>0` = length(which(Value > 0)) / length(Value),
            `P<0` = length(which(Value < 0)) / length(Value)) %>%
  mutate(Name = str_replace(Parameter, "(.*)(\\[.*)", "\\1"),
         Number = as.numeric(str_replace(Parameter, 
                                         "(.*\\[)(\\d+)(\\])", "\\2"))) %>%
  arrange(Name, Number) %>%
  select(-Name, -Number)
alphaMod4 <- sumMod4$Mean[str_detect(sumMod4$Parameter, "alpha")]
betaMod4 <- sumMod4$Mean[str_detect(sumMod4$Parameter, "beta")]
piMod4 <- sumMod4$Mean[str_detect(sumMod4$Parameter, "pie")]
diagMod4 <- tibble(y = y,
                   pi = piMod4, 
                   logitPi = log(pi / (1 - pi)),
                   SINCEHIV = x[, 2],
                   a2 = alphaMod4[2],
                   color = "1") %>%
  mutate(xa = SINCEHIV * a2)
grid.arrange(ggplot(diagMod2, aes(x = SINCEHIV, y = pi, color = "black")) +
  geom_point() +
  geom_smooth(method = "loess", se = FALSE) +
  geom_point(aes(y = y, color = "blue")) +
  geom_smooth(aes(y = y, color = "blue"), method = "loess", se = FALSE) +
  labs(y = "", title = "Model 2: Pi and Y against Time Since HIV Diagnosis",
       x = "Time Since HIV (yr)") +
  scale_color_manual(name = 'Y Axis', 
         values =c('black'='black','blue'='blue'), labels = c('Pi','Health Info')),
  ggplot(diagMod4, aes(x = SINCEHIV, y = pi, color = "black")) +
  geom_point() +
  geom_smooth(method = "loess", se = FALSE) +
  geom_point(aes(y = y, color = "blue")) +
  geom_smooth(aes(y = y, color = "blue"), method = "loess", se = FALSE) +
  labs(y = "", title = "Model 4: Pi and Y against Time Since HIV Diagnosis",
       x = "Time Since HIV (yr)") +
  scale_color_manual(name = 'Y Axis', 
         values =c('black'='black','blue'='blue'), labels = c('Pi','Health Info')))

```

```{r results, include = TRUE}
kable(sumMod4 %>%
        filter(str_detect(Parameter, "alpha|sigma")) %>%
        mutate(Covariate = c(table2$Parameter[-3], "Site")) %>%
        select(Covariate, everything()),
      digits = 2, caption = "Table 4. Model Estimates") %>%
  kable_styling(bootstrap_options = c("striped", "condensed"),
                full_width = FALSE)
```

```{r plotPosterior, include = TRUE, fig.cap = "Figure "}
priorMeans <- table2$Mean[-3]
priorX <- double(304800)
likeliX <- double(304800)
likeliMod <- lm(HealthInfo ~ SINCEHIV + Gender_Woman + Gender_Other +
                  Ed_Higher + Race_Black + Race_White + Race_Other +
                  Employ_Student + Employ_Employed + Employ_Disabled + 
                  Employ_Other, 
                 data = bind_cols(
                   tibble(HealthInfo = y), 
                   as.tibble(x[, c(-1 ,-3)])))
likeliMeans <- likeliMod$coefficients
likeliSDs <- summary(likeliMod)$coefficients[, "Std. Error"]
for (i in 1:length(priorMeans)) {
  priorX[(25400*i - 25399):(25400*i)] <- 
    rnorm(25400, as.numeric(priorMeans[i]), 1)
  likeliX[(25400*i - 25399):(25400*i)] <- rnorm(25400, 
                                                likeliMeans[i],
                                                likeliSDs[i])
}
alphaNames <- paste0("alpha[", 1:12, "]") %>%
  setNames(colnames(x[, -3]))
postMod4 <- burnMod4$Burnin.sims.matrix %>%
  as.data.frame() %>%
  select(contains("alpha")) %>%
  gather("Key", "Posterior") %>%
  mutate(Key = fct_recode(factor(Key, levels = unique(Key)),
                                 !!!alphaNames),
         Prior = priorX,
         Likelihood = likeliX)
ggplot(postMod4 %>%
         filter(Key == "SINCEHIV"),
       aes(x = Posterior, fill = "posterior")) +
  geom_density() +
  geom_density(aes(x = Prior, fill = "prior")) +
  geom_density(aes(x = Likelihood, fill = "likeli")) +
  scale_x_continuous(limits = c(-2, 0.1)) +
  # scale_y_continuous(limits = c(0, 20)) +
  scale_fill_manual(name = "Distribution",
                     values = c("likeli" = "red",
                                "posterior" = "green", 
                                "prior" = "blue"),                     
                     labels = c("Likelihood", "Posterior", "Prior")) +
  labs(y = "Density", x = "Time Since HIV Coefficient",
       title = "Time Since HIV Regression Coefficient Distributions")
ggplot(postMod4 %>%
         filter(Key == "SINCEHIV") %>%
         gather("Distribution", "Data", -Key),
       aes(x = Data, fill = Distribution)) +
  facet_grid(.~Distribution, scales = "free") +
  geom_density() +
  labs(y = "Density", x = "Time Since HIV Coefficient",
       title = "Time Since HIV Regression Coefficient Distributions")
```

